\cvsection{Experience}
\begin{cventries}
  \cventry
    {Automation Engineer}
    {Deliverect}
    {Madrid, Spain}
    {2022 - Present}
    {\begin{cvitems}
      \item {Automate business processes end-to-end, leveraging custom scripting, workflow orchestration, and Generative AI.}
      \item {Designed a quote validation tool using FastAPI and Vertex AI, integrating complex rules with a TypeScript UI and BigQuery telemetry.}
      \item {Managing critical automations via Apache Airflow, synchronizing data across NetSuite, HubSpot, and Planhat.}
      \item {Developed a synchronous onboarding service for reselling partners using FastAPI and PostgreSQL.}
      \item {Collaborated with the AI team to build an intelligent chat system using Microsoft Semantic Kernel for automated account actions.}
      \item {Optimized CI/CD pipelines with GitHub Actions, SonarQube, and AI-driven dev tools (Claude Code, Gemini CLI).}
    \end{cvitems}}
  \cventry
    {Software Engineer (Backend \& Frontend)}
    {GMV Aerospace and Defence}
    {Madrid, Spain}
    {2019 - 2022}
    {\begin{cvitems}
      \item {Developed robust backend solutions using C\# and .NET Core for the defense sector.}
      \item {Built dynamic frontend applications using Angular and React.}
      \item {Managed full software lifecycle tasks, from requirement analysis to technical documentation.}
    \end{cvitems}}
  \cventry
    {Collaborator \& Research Intern}
    {SABIEN (ITACA - UPV)}
    {Valencia, Spain}
    {2016 - 2018}
    {\begin{cvitems}
      \item {Developed a mobile application for oncology patients.}
      \item {Conducted systematic reviews of healthcare systems, leading to a published research paper.}
      \item {Completed a 6-month research internship focused on technological innovations for healthcare.}
    \end{cvitems}}
\end{cventries}